---
title: "Proyecto final módulo 5 - Win Predictor - manipulacion de base de datos"
author: "Alexis_Oscar"
output: html_document:
  theme:journal
  toc:true
  toc:true
  toc_float:
    collapsed:true
    
---

# initial

Objective: Chess Game Outcome Predictor
Build a model that predicts the winner (White/Black/Draw) based on the first 10-15 moves of a game. Use features like opening type, player rating difference, time control, and move quality scores. This could help players understand critical early-game positions and their winning probabilities.
ML Approach: Classification using Random Forest, XGBoost, or Neural Networks
Features: Opening ECO codes, rating gaps, move timestamps, piece development metrics


```{r}
library(dplyr)
library(readr)
library(ggplot2)
library(skimr)
library(lubridate)
library(stringr)
library(tidyr)
#library(tidyverse) #
library(purrr)
library(stringi)


options(scipen = 999)

```

# loads

## load data 

```{r}
chess_db <- 
  readr::read_csv("games.csv") %>% 
  group_by(id) %>% 
  mutate(row_index = row_number()) %>% 
  ungroup %>% 
  filter(row_index == 1)

head(chess_db)
```

## skim db

```{r}

chess_db %>% glimpse

chess_db %>% 
skim() %>% 
    tibble::as_tibble() 

```

## tests 
```{r}

chess_db %>% 
  filter(rated==TRUE) %>% 
#  mutate(opening_class = str_sub(opening_eco,1,1)) %>% 
  group_by( increment_code) %>% tally %>% arrange(desc(n))

chess_db %>% 
  filter(id =='QurxyQkA')
```

## ad-hoc functions

```{r}

identify_chess_moves <- function(moves_string) {
  # Split moves by whitespace
  moves <- str_split(moves_string, "\\s+")[[1]]
  
  # Remove empty strings
  moves <- moves[moves != ""]
  
  # Separate white and black moves
  white_moves <- moves[seq(1, length(moves), 2)]  # Odd positions (1, 3, 5, ...)
  black_moves <- moves[seq(2, length(moves), 2)]  # Even positions (2, 4, 6, ...)
  
  #Find  turns
  white_castle_turn <- NA
  black_castle_turn <- NA
  
  white_first_check_turn <- NA
  black_first_check_turn <- NA
  
  white_checks_limited_count <- 0
  black_checks_limited_count <- 0
  
  white_loss_before_five <- 0
  black_loss_before_five <- 0
  
  white_loss_before_ten <- 0
  black_loss_before_ten <- 0
  
  white_loss_before_fifteen <- 0
  black_loss_before_fifteen <- 0
  
  #Check for castling moves (O-O for kingside, O-O-O for queenside)
  for (i in seq_along(white_moves)) {
    if (str_detect(white_moves[i], "^O-O(-O)?$")) {
      white_castle_turn <- i
      break
    }
  }

  for (i in seq_along(black_moves)) {
    if (str_detect(black_moves[i], "^O-O(-O)?$")) {
      black_castle_turn <- i
      break
    }
  }
  
  for (i in seq_along(white_moves)) {
    if (str_detect(white_moves[i], "\\+")) {
      white_first_check_turn <- i
      break
    }
  }

  for (i in seq_along(black_moves)) {
    if (str_detect(black_moves[i], "\\+")) {
      black_first_check_turn <- i
      break
    }
  }
  
  
  for (i in seq_along(white_moves)) {
    if (i < 16 & str_detect(white_moves[i], "\\+")) {
      white_checks_limited_count <- white_checks_limited_count + 1
    }
  }
  
  for (i in seq_along(black_moves)) {
    if (i < 16 & str_detect(black_moves[i], "\\+")) {
      black_checks_limited_count <- black_checks_limited_count + 1
    }
  }
  
  ## Capture or loss pieces _whites
  
  for (i in seq_along(white_moves)) {
    if (i < 6 & str_detect(white_moves[i], "x")) {
      black_loss_before_five <- black_loss_before_five + 1
    }
  }
  
  for (i in seq_along(white_moves)) {
    if (i < 11 & str_detect(white_moves[i], "x")) {
      black_loss_before_ten <- black_loss_before_ten + 1
    }
  }
  
  for (i in seq_along(white_moves)) {
    if (i < 16 & str_detect(white_moves[i], "x")) {
      black_loss_before_fifteen <- black_loss_before_fifteen + 1
    }
  }
  
  ## Capture or loss pieces _black
  
  for (i in seq_along(black_moves)) {
    if (i < 6 & str_detect(black_moves[i], "x")) {
      white_loss_before_five <- white_loss_before_five + 1
    }
  }
  
  for (i in seq_along(black_moves)) {
    if (i < 11 & str_detect(black_moves[i], "x")) {
      white_loss_before_ten <- white_loss_before_ten + 1
    }
  }
  
  for (i in seq_along(black_moves)) {
    if (i < 16 & str_detect(black_moves[i], "x")) {
      white_loss_before_fifteen <- white_loss_before_fifteen + 1
    }
  }
  
  
  #Check for check moves
  
  return(list(
    white_moves = paste(white_moves, collapse = " "),
    black_moves = paste(black_moves, collapse = " "),
    white_castle_turn = white_castle_turn,
    black_castle_turn = black_castle_turn,
    white_first_check_turn = white_first_check_turn,
    black_first_check_turn = black_first_check_turn,
    white_checks_limited_count = white_checks_limited_count,
    black_checks_limited_count = black_checks_limited_count,
    white_loss_before_five = white_loss_before_five,
    white_loss_before_ten = white_loss_before_ten,
    white_loss_before_fifteen = white_loss_before_fifteen,
    black_loss_before_five = black_loss_before_five,
    black_loss_before_ten = black_loss_before_ten,
    black_loss_before_fifteen = black_loss_before_fifteen
    
  ))
}


```

 
# final munged
 
## players db 

```{r}

#queremos quedarnos solo con rated? esto significa que esta partida afecta el ELO o el rating del jugador; creo que es un si? 	TRU: 16155, FAL: 3903

whites_db <-
  chess_db %>% 
  summarise(
    .by = c(white_id)
    , as_white_games_count = n()
    , as_white_wins = sum(if_else(winner == 'white',1,0),na.rm=T )
    , as_white_loss = sum(if_else(winner == 'black',1,0),na.rm=T )
    , as_white_draw = sum(if_else(winner == 'draw',1,0),na.rm=T )
  ) %>% 
  left_join(
    chess_db %>% 
      mutate(opening_class = str_sub(opening_eco,1,1)) %>% 
      summarise(.by = c(white_id,opening_class), moves = n()) %>% 
      group_by(white_id) %>% 
      arrange(desc(moves)) %>% 
      mutate(row_index = row_number()) %>% ungroup %>%
      filter(row_index == 1) %>% 
      select(white_id,as_white_fav_opening_class = opening_class)
  ) %>% 
  left_join(
    chess_db %>% 
      mutate(opening_class = str_sub(opening_eco,1,1)) %>% 
      summarise(.by = c(white_id,opening_eco), moves = n()) %>% 
      group_by(white_id) %>% 
      arrange(desc(moves)) %>% 
      mutate(row_index = row_number()) %>% ungroup %>%
      filter(row_index == 1) %>% 
      select(white_id,as_white_fav_opening_eco = opening_eco)
  )
  

blacks_db <-
  chess_db %>% 
  summarise(
    .by = c(black_id)
    , as_black_games_count = n()
    , as_black_wins = sum(if_else(winner == 'black',1,0),na.rm=T )
    , as_black_loss = sum(if_else(winner == 'white',1,0),na.rm=T )
    , as_black_draw = sum(if_else(winner == 'draw',1,0),na.rm=T )
  ) 


player_bcv <-
  chess_db %>% 
      group_by(white_id) %>% 
      arrange(desc(created_at)) %>% 
      mutate(row_index = row_number()) %>% ungroup %>%
      filter(row_index == 1) %>% 
      select(white_id,as_white_elo = white_rating,white_created_at = created_at) %>% 
  full_join(
      chess_db %>% 
      group_by(black_id) %>% 
      arrange(desc(created_at)) %>% 
      mutate(row_index = row_number()) %>% ungroup %>%
      filter(row_index == 1) %>% 
      select(black_id , as_black_elo = black_rating , black_created_at = created_at) 
      ,by = c("white_id"= "black_id")
      ) %>% 
    mutate(across(where(is.numeric), ~tidyr::replace_na(.x, 0))) %>% 
    mutate(
      last_elo = if_else(white_created_at >= black_created_at,as_white_elo,as_black_elo)
      ,last_elo_band = case_when(
        last_elo <= 1200 ~ 0,
        last_elo <= 1400 ~ 1,
        last_elo <= 1600 ~ 2,
        last_elo <= 1800 ~ 3,
        last_elo <= 2000 ~ 4,
        last_elo <= 2200 ~ 5,
        TRUE ~ 6
      )
    ) %>% 
    select(white_id,last_elo,last_elo_band) ## should we add the fav game style (most played) and which is the win rate in that game style?

player_munged_db<-
  whites_db %>% 
    full_join(
      blacks_db,
      by = c("white_id"= "black_id")
      ) %>% 
    mutate(across(where(is.numeric), ~tidyr::replace_na(.x, 0))) %>% 
    mutate(
       total_games_count = as_white_games_count + as_black_games_count
      ,total_wins = as_white_wins + as_black_wins
      ,total_loss = as_white_loss + as_black_loss
      ,total_draw = as_white_draw + as_black_draw
      ,as_white_winrate = if_else(as_white_games_count==0,0,round(as_white_wins/as_white_games_count,8))
      ,as_black_winrate = if_else(as_black_games_count==0,0,round(as_black_wins/as_black_games_count,8))
      ,total_winrate = if_else(total_games_count==0,0,round(total_wins/total_games_count,8))
    ) %>% 
  left_join(
    player_bcv
  ) ## do we need a band for total games played?
  

player_munged_db %>% 
  arrange(desc(total_games_count))

#how do we define ??

write.csv(
  player_munged_db,
  "player_munged_db.csv",
  row.names = F
)

```
 

## main db 


```{r}

#desduplicamos los id al principio, nos quedamos con 19,113

#queremos quedarnos solo con rated? esto significa que esta partida afecta el ELO o el rating del jugador; creo que es un si? 80% TRU: 15467, FAL: 3646

#queremos quedarnos con alguna banda de total de jugadas? mas de 5 partidas? para mi es en uno

# queremos quitar partidas de mas de x horas? y quitar que duran menos de x horas? estaba pensando que necesitamos al menos 32 turnos, 16 turnos cada quien.

# Preguntas a resolver
## si la partida es blitz, o bullet, con menos de 20 movimientos total? como predigo
## si la partida es de mayor, como predigo?


# chess_db %>% 
#   mutate(
#     opening_class_letters = str_sub(opening_eco,1,1)  # clasifica aperturas A-flank, B-semi open, C-Open, D-closed, E-indian defence
#     ,opening_class = case_when(
#       opening_class_letters == 'A' ~ 0, 
#       opening_class_letters == 'B' ~ 1, 
#       opening_class_letters == 'C' ~ 2, 
#       opening_class_letters == 'D' ~ 3, 
#       opening_class_letters == 'E' ~ 4,
#       TRUE ~ 5
#     ),
#     ,opening_eco_mod = as.numeric(paste(opening_class,str_sub(opening_eco,2,3),sep ='') )
#   ) %>% View


chess_munged_db <-
  chess_db %>% 
    filter(
   # rated == TRUE &
     turns > 31
    & winner %in% c('white','black') #remove later?
  ) %>% ##head
    mutate(
      moves_analysis = map(moves,identify_chess_moves)
    ) %>% 
    unnest_wider(moves_analysis) %>%
   tidyr::separate(increment_code, into = c("before_plus", "after_plus"), sep = "\\s*\\+\\s*", remove = FALSE) %>% 
  mutate(
    # winner = case_when(
    #   winner == "white" ~ 0,
    #   winner == "black" ~ 1,
    #   TRUE ~ 2
    # ),
    opening_class_letters = str_sub(opening_eco,1,1)  # clasifica aperturas A-flank, B-semi open, C-Open, D-closed, E-indian defence
    ,opening_class = case_when(
      opening_class_letters == 'A' ~ 0, 
      opening_class_letters == 'B' ~ 1, 
      opening_class_letters == 'C' ~ 2, 
      opening_class_letters == 'D' ~ 3, 
      opening_class_letters == 'E' ~ 4,
      TRUE ~ 5
    ),
    ,opening_eco_mod = as.numeric(paste(opening_class,str_sub(opening_eco,2,3),sep ='') )
    ,base_time = as.numeric(str_trim(before_plus))
    ,add_time = as.numeric(str_trim(after_plus))
    ,total_time = round(base_time +(add_time* turns/60),0)
    ,game_class = case_when( #basamos en base time ; summarise(.by = game_class, game_min = min(total_time),game_max = max(total_time)) 
      base_time <3 ~ 0,
      base_time <11 ~ 1,
      base_time <31 ~ 2,
      base_time <181 ~ 3,
      TRUE ~ 4
    )
    ,rating_dif = white_rating - black_rating
    ,white_elo_band = case_when(
        white_rating <= 1200 ~ 0,
        white_rating <= 1400 ~ 1,
        white_rating <= 1600 ~ 2,
        white_rating <= 1800 ~ 3,
        white_rating <= 2000 ~ 4,
        white_rating <= 2200 ~ 5,
        TRUE ~ 6
      )
    ,black_elo_band = case_when(
        black_rating <= 1200 ~ 0,
        black_rating <= 1400 ~ 1,
        black_rating <= 1600 ~ 2,
        black_rating <= 1800 ~ 3,
        black_rating <= 2000 ~ 4,
        black_rating <= 2200 ~ 5,
        TRUE ~ 6
      )
    ,same_elo_band_flag = if_else(white_elo_band == black_elo_band,1,0 )
    ,same_elo_step_flag = if_else(abs(rating_dif) <200,1,0 )
    
    ,white_castle_turn_limited = if_else(is.na(white_castle_turn),0, if_else(white_castle_turn<= 15, white_castle_turn,NA)) 
    ,white_castle_before_five = if_else(is.na(white_castle_turn),0, if_else(white_castle_turn<= 5, 1,0)) 
    ,white_castle_before_ten = if_else(is.na(white_castle_turn),0, if_else(white_castle_turn<= 10, 1,0)) 
    ,white_castle_before_fifteen = if_else(is.na(white_castle_turn),0, if_else(white_castle_turn<= 15, 1,0)) 
    
    ,black_castle_turn_limited = if_else(is.na(black_castle_turn),0, if_else(black_castle_turn<= 15, black_castle_turn,NA)) 
    ,black_castle_before_five = if_else(is.na(black_castle_turn),0, if_else(black_castle_turn<= 5, 1,0)) 
    ,black_castle_before_ten = if_else(is.na(black_castle_turn),0, if_else(black_castle_turn<= 10, 1,0)) 
    ,black_castle_before_fifteen = if_else(is.na(black_castle_turn),0, if_else(black_castle_turn<= 15, 1,0)) 
    
    ,white_checks_before_fifteen = if_else(is.na(white_first_check_turn),0, if_else(white_first_check_turn<= 15, 1,0)) 
    ,white_checks_before_ten = if_else(is.na(white_first_check_turn),0, if_else(white_first_check_turn<= 10, 1,0)) 
    ,white_checks_before_five = if_else(is.na(white_first_check_turn),0, if_else(white_first_check_turn<= 5, 1,0)) 
    
    ,black_checks_before_fifteen = if_else(is.na(black_first_check_turn),0, if_else(black_first_check_turn<= 15, 1,0))
    ,black_checks_before_ten = if_else(is.na(black_first_check_turn),0, if_else(black_first_check_turn<= 10, 1,0))
    ,black_checks_before_five = if_else(is.na(black_first_check_turn),0, if_else(black_first_check_turn<= 5, 1,0))
    
    
  ) #%>% glimpse   # head(n =10)    #skim()  #group_by(total_time) %>% tally %>% arrange(desc(total_time))


final_chess_munged_db <-
  chess_munged_db %>% 
    select(
       id
      ,white_id
      ,black_id
      ,winner
      ,base_time
      ,add_time
      ,total_time
      ,game_class
      ,opening_class
      ,opening_eco_mod
      ,rating_dif
      ,same_elo_band_flag
      ,same_elo_step_flag

      ,white_elo_band
      ,white_castle_turn_limited
      ,white_castle_before_five
      ,white_castle_before_ten
      ,white_castle_before_fifteen
      ,white_checks_limited_count
      ,white_checks_before_five
      ,white_checks_before_ten
      ,white_checks_before_fifteen
      ,white_loss_before_five
      ,white_loss_before_ten
      ,white_loss_before_fifteen
      
      ,black_elo_band
      ,black_castle_turn_limited
      ,black_castle_before_five
      ,black_castle_before_ten
      ,black_castle_before_fifteen
      ,black_checks_before_five
      ,black_checks_before_ten
      ,black_checks_before_fifteen
      ,black_checks_limited_count
      ,black_loss_before_five
      ,black_loss_before_ten
      ,black_loss_before_fifteen
      
      
    ) %>% 
    left_join(
      player_munged_db %>%
        select(
          white_id
          ,player_as_white_fav_opening_class = as_white_fav_opening_class
          ,player_as_white_fav_opening_eco = as_white_fav_opening_eco
          #,player_as_white_winrate = as_white_winrate
          #,player_as_white_games_count = as_white_games_count
          ,player_white_total_games_count = total_games_count
          #,player_white_total_winrate = total_winrate
          #,white_last_elo = last_elo
          #,white_last_elo_band = last_elo_band
        )
      ,by = c("white_id" = "white_id")
    ) %>% 
    left_join(
      player_munged_db %>% 
        select(
          white_id
          #,player_as_black_winrate = as_black_winrate
          #,player_as_black_games_count = as_black_games_count
          ,player_black_total_games_count = total_games_count
          #,player_black_total_winrate = total_winrate
          #,white_last_elo = last_elo
          #,white_last_elo_band = last_elo_band
        )
      ,by = c("black_id" = "white_id")
    ) %>% 
    select(
      -white_id
      ,-black_id
      
      )
  

#hist(player_munged_db$white_first_check_turn)  


## how many checks? first check who? first check at which move?
##do we want bands for turns? or game bands are enough?


#que le pegamos de player?


write.csv(
  final_chess_munged_db,
  "final_chess_munged_db.csv",
  row.names = F
)

```





## DB for modeling without feature engineering. 


```{r}

#desduplicamos los id al principio, nos quedamos con 19,113

#queremos quedarnos solo con rated? esto significa que esta partida afecta el ELO o el rating del jugador; creo que es un si? 80% TRU: 15467, FAL: 3646

#queremos quedarnos con alguna banda de total de jugadas? mas de 5 partidas? para mi es en uno

# queremos quitar partidas de mas de x horas? y quitar que duran menos de x horas? estaba pensando que necesitamos al menos 32 turnos, 16 turnos cada quien.

# Preguntas a resolver
## si la partida es blitz, o bullet, con menos de 20 movimientos total? como predigo
## si la partida es de mayor, como predigo?


# chess_db %>% 
#   mutate(
#     opening_class_letters = str_sub(opening_eco,1,1)  # clasifica aperturas A-flank, B-semi open, C-Open, D-closed, E-indian defence
#     ,opening_class = case_when(
#       opening_class_letters == 'A' ~ 0, 
#       opening_class_letters == 'B' ~ 1, 
#       opening_class_letters == 'C' ~ 2, 
#       opening_class_letters == 'D' ~ 3, 
#       opening_class_letters == 'E' ~ 4,
#       TRUE ~ 5
#     ),
#     ,opening_eco_mod = as.numeric(paste(opening_class,str_sub(opening_eco,2,3),sep ='') )
#   ) %>% View


chess_munged_db <-
  chess_db %>% 
   filter(
     winner %in% c('white','black') #remove later?
     # & rated == TRUE 
     # & turns > 31
  ) %>% 
  tidyr::separate(increment_code, into = c("before_plus", "after_plus"), sep = "\\s*\\+\\s*", remove = FALSE) %>% 
  mutate(
     rated = as.numeric(rated)
     ,rating_dif_abs = abs(white_rating - black_rating)
     ,rating_dif_class = case_when(
       white_rating - black_rating >10 ~ 1,
       black_rating - white_rating >10 ~ -1,
       TRUE ~ 0
     )
    # ,rating_dif_winner = case_when(   ## this implies we know who the winner is
    #   winner == 'white' ~ white_rating - black_rating,
    #   winner == 'black' ~ black_rating - white_rating,
    #   TRUE ~ NA
    # )
    ,opening_class_letters = str_sub(opening_eco,1,1)  # clasifica aperturas A-flank, B-semi open, C-Open, D-closed, E-indian defence
    ,opening_class = case_when(
      opening_class_letters == 'A' ~ 0, 
      opening_class_letters == 'B' ~ 1, 
      opening_class_letters == 'C' ~ 2, 
      opening_class_letters == 'D' ~ 3, 
      opening_class_letters == 'E' ~ 4,
      TRUE ~ 5
    ),
    ,opening_eco_mod = as.numeric(paste(opening_class,str_sub(opening_eco,2,3),sep ='') )
    ,base_time = as.numeric(str_trim(before_plus))
    ,add_time = as.numeric(str_trim(after_plus))
    ,total_time = round(base_time +(add_time* turns/60),0)
    ,victory_status_class = case_when(
      victory_status == 'mate' ~ 1,
      victory_status == 'resign' ~ 0,
      victory_status == 'outoftime' ~ 0,
    )
  ) %>% 
  select(
    id
    ,winner
    ,rated 
    ,victory_status_class
    ,base_time
    ,add_time
    ,total_time
    ,white_rating
    ,black_rating
    ,rating_dif_abs
    ,rating_dif_class
    ,opening_class
    ,opening_eco_mod
    ,opening_ply
  ) 
  

#hist(player_munged_db$white_first_check_turn)  


write.csv(
  chess_munged_db,
  "basic_chess_munged_db.csv",
  row.names = F
)

```

## DB for modeling with some data wrangling on the current columns

```{r}

chess_munged_db <-
  chess_db %>% 
    filter(
       winner %in% c('white','black') 
   # rated == TRUE &
   #  turns > 31
  ) %>% 
   tidyr::separate(increment_code, into = c("before_plus", "after_plus"), sep = "\\s*\\+\\s*", remove = FALSE) %>% 
  mutate(
    rated = as.numeric(rated)
    ,opening_class_letters = str_sub(opening_eco,1,1)  # clasifica aperturas A-flank, B-semi open, C-Open, D-closed, E-indian defence
    ,opening_class = case_when(
      opening_class_letters == 'A' ~ 0, 
      opening_class_letters == 'B' ~ 1, 
      opening_class_letters == 'C' ~ 2, 
      opening_class_letters == 'D' ~ 3, 
      opening_class_letters == 'E' ~ 4,
      TRUE ~ 5
    ),
    victory_status_class = case_when(
      victory_status == 'mate' ~ 1,
      victory_status == 'resign' ~ 0,
      victory_status == 'outoftime' ~ 0,
    )
    ,opening_eco_mod = as.numeric(paste(opening_class,str_sub(opening_eco,2,3),sep ='') )
    ,base_time = as.numeric(str_trim(before_plus))
    ,add_time = as.numeric(str_trim(after_plus))
    ,total_time = round(base_time +(add_time* turns/60),0)
    ,game_class = case_when( #basamos en base time ; summarise(.by = game_class, game_min = min(total_time),game_max = max(total_time)) 
      base_time <3 ~ 0,
      base_time <11 ~ 1,
      base_time <31 ~ 2,
      base_time <181 ~ 3,
      TRUE ~ 4
    )
    ,rating_dif_abs = abs(white_rating - black_rating)
     ,rating_dif_class = case_when(
       white_rating - black_rating >10 ~ 1,
       black_rating - white_rating >10 ~ -1,
       TRUE ~ 0
     )
    # ,rating_dif_winner = case_when(   ## this implies we know who the winner is
    #   winner == 'white' ~ white_rating - black_rating,
    #   winner == 'black' ~ black_rating - white_rating,
    #   TRUE ~ NA
    # )
    ,white_elo_band = case_when(
        white_rating <= 1200 ~ 0,
        white_rating <= 1400 ~ 1,
        white_rating <= 1600 ~ 2,
        white_rating <= 1800 ~ 3,
        white_rating <= 2000 ~ 4,
        white_rating <= 2200 ~ 5,
        TRUE ~ 6
      )
    ,black_elo_band = case_when(
        black_rating <= 1200 ~ 0,
        black_rating <= 1400 ~ 1,
        black_rating <= 1600 ~ 2,
        black_rating <= 1800 ~ 3,
        black_rating <= 2000 ~ 4,
        black_rating <= 2200 ~ 5,
        TRUE ~ 6
      )
    ,same_elo_band_flag = if_else(white_elo_band == black_elo_band,1,0 )
    ,same_elo_step_flag = if_else(abs(rating_dif_abs) <100,1,0 )
    ) 


final_chess_munged_db <-
  chess_munged_db %>% 
    select(
     id
    ,winner
    ,rated 
    ,victory_status_class
    ,base_time
    ,add_time
    ,total_time
    ,white_rating
    ,black_rating
    ,rating_dif_abs
    ,rating_dif_class
    ,opening_class
    ,opening_eco_mod
    ,opening_ply
      ,game_class
      ,same_elo_band_flag
      ,same_elo_step_flag
      ,white_elo_band
      ,black_elo_band
    ) 
  

#hist(player_munged_db$white_first_check_turn)  


write.csv(
  final_chess_munged_db,
  "altered_chess_munged_db.csv",
  row.names = F
)

```




```{r}
final_chess_munged_db %>% 
  group_by(game_class) %>% tally
```

